Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints

### 2025-04-06 manuscript.tex
update; figures and notations

Consider an uncertain Euler-Lagrange system modeled as
\begin{equation}
    \mm M\ddq + \mm V_m + \mm F + \mm G + \mv\tau_d
    =
    \mysat(\mv\tau)
    \label{eq:sys1}
\end{equation}
where $\q\in \R^n$ denotes the generalized coordinate, $\mv \tau_d$ represents disturbance and $\mv\tau\in\R^n$ denotes the control input. 
The terms $\mm M:=\mm M(\q)\in\R^{n\times n}$, $\mm V_m:=\mm V_m(\q,\dq)\in\R^{n\times n}$, $\mm F:=\mm F(\dq)\in\R^{n}$ and $\mm G:=\mm G(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators and is defined as 
\begin{equation}
    \mysat(\mv\tau)
    :=
    \begin{cases}
        \mv\tau, 
        & 
        \text{if } \Vert\mv\tau\Vert\le \bar\tau,
        \\
        \bar\tau
        \cdot
        \tfrac{\mv\tau}{\Vert\mv\tau\Vert}, 
        & 
        \text{otherwise},
    \end{cases}
    \label{eq:sat}
\end{equation}
where $\bar\tau$ denotes the maximum norm of control input.
To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
Appendix \ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.

@@

Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \mm M\fe$. 
Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
\begin{equation}
    \begin{aligned}
        \ddtt{V}_1
        =&
        \fe^\top \mm M (
            -\mm V_m \fe -\mm K \fe + \mv f
            -\mv \tau_d + \mysat(\mv\tau)
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top \dot{\mm M}\fe
        \\
        =&
        -
        \fe^\top \mm K \fe 
        +
        \fe^\top (
            \mv f+\mysat(\mv\tau)
            -\mv \tau_d
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top(\dot{\mm M}- 2\mm V_m)\fe
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \bar\tau_d\norm{\fe}
        +
        \fe^\top (\mv f+\mysat(\mv \tau))
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \bar\tau_d\norm{\fe}
        +
        \fe^\top (\mysat(\mv\tau)-\mv\tau^*)
        ,
    \end{aligned}
    \label{eq:lya1:dot1}
\end{equation}
where $\mv\tau^*:= -\mv f$ is the ideal control input whose maximum norm is $\bar\tau$ according to Assumption \ref{assum:feasible} and \eqref{eq:sat}. 
Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_{\min}(\mm K)}$, if $\mv \tau=-\mv\tau^*$ can be realized.
However, $\mv \tau^*$ is not available in practice, since $\mv f$ is unknown.

@@

% ------------------------------------
% Robot Model and Reference Trajectory
% ------------------------------------
The proposed CoNAC was validated using a two-link manipulator model, as depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{Markus:2013aa}. 
The system dynamics of the two-link manipulator is described by the following equations:
\MSRY{ADD MORE DETAIL; Following Eqn is just example}
\begin{equation}
    \begin{aligned}
        \mm M(\q) \ddtt{\q} + \mm V_m(\q,\dot\q) + \mm F(\q,\dot\q) + \mm G(\q) = \mv\tau,
        \\
        \mv\tau = \estNN(\q,\dot\q),
    \end{aligned}
    \label{eq:robot_dynamics}
\end{equation}
The parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ \MSRY{more parameters} denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
The values of the system model parameters are provided in Table~\ref{table:system:params}. 
The desired trajectory for $\q=[q_1,q_2]^\top $ was defined with \MSRY{5th Poly functions} as
\begin{equation}
  {q_d}(t) = 
  \begin{bmatrix}
      {q_d}_1\\{q_d}_2
  \end{bmatrix}
  =
  \begin{cases}
    \mypoly(\q_0,\q_1,t_f,t)
      & \text{if } 0\le t < t_f \\
    \mypoly(\q_1,\q_2,t_f,t-t_f)
      & \text{if } t_f\le t < 2t_f \\
    \mypoly(\q_2,\q_3,t_f,t-2t_f)
      & \text{if } 2t_f\le t < 3t_f \\
    \mypoly(\q_3,\q_0,t_f,t-3t_f)
      & \text{if } 3t_f\le t < 4t_f \\
  \end{cases}
  ,
  \label{eq:desired trajectory}
\end{equation}
where \MSRY{CAN BE CHANGED}$\q_0=[0,0]^\top$, $\q_1=[\pi/2,\pi/2]^\top$, $\q_2=[\pi/2,0]^\top$, $\q_3=[0,\pi/2]^\top$, and $t_f=5$ s.
\MSRY{VIDEO IS PROVIDED; IF WE CAN PROVIDE}

% ------------------------------------
% Control Input Saturation
% ------------------------------------
To demonstrate the effectiveness of the proposed CoNAC to handle the combination of the nonlinear input constraints, the following control input saturations were imposed:
\begin{equation}
  \mysat(\mv\tau) 
  =
  ,
  \label{eq:control input saturation}
\end{equation}
where $\bar\tau=50, \bar\tau_1$ and $\bar\tau_2$ are the saturation limit values for the norm of the control input and the first and second links, respectively.

@@

% ------------------------------------
% Controller Table
% ------------------------------------
\begin{table}[t]
  \renewcommand{\arraystretch}{1.3}
  \caption{Properties of the controllers used in simulation}
  \label{table:controller}
  \centering
  \begin{tabular}{c c c}
  \hline
  & \multicolumn{2}{c}{\bf{Handling Capability}}\\
  \hline
  \hline
  & Weight Norm Constraint & Input Norm Constraint\\
  \hline
  \hline
  \multirow{2}{*}{\bf{CoNAC}} & O & $\triangle$ \\
     & (by projection) &  (by aux. system)\\
  \hline
  \multirow{2}{*}{\bf{NAC-AUX}} & O & O\\
     & (by optimization) & (by optimization)\\
  \hline
  \end{tabular}
\end{table}

@@

\begin{figure}[t]
  \centering
    \subfloat[Tracking result of $d$-axis stator current .]{
      \includegraphics[width=\figSize\linewidth]
      {
        src/mearsurement/figures/Fig1.eps
      }%
      \label{fig:ctrl:result:q1}}
    \vspace{2mm}
    \subfloat[Tracking result of $d$-axis stator current .]{
      \includegraphics[width=\figSize\linewidth]
      {
        src/mearsurement/figures/Fig2.eps
      }%
      \label{fig:ctrl:result:q2}}
    \vspace{2mm}
      \subfloat[Control input.]{
        \includegraphics[width=\figSize\linewidth]
        {
          src/mearsurement/figures/Fig3.eps
        }%
        \label{fig:ctrl:result:tau:1}}
    \vspace{2mm}
      \subfloat[Control input.]{
        \includegraphics[width=\figSize\linewidth]
        {
          src/mearsurement/figures/Fig4.eps
        }%
        \label{fig:ctrl:result:tau:2}}
  \caption{
  Simulation results of the CoNAC (blue) and NAC-AUX (cyan), and reference signal of ${\q}_d$ (red dashed line).
  }
\label{fig:ctrl:result}
\end{figure}

\begin{figure}[t]
  \centering
    \subfloat[Tracking result of $d$-axis stator current .]{
      \includegraphics[width=\figSize\linewidth]
      {
        src/mearsurement/figures/Fig5.eps
      }%
      \label{fig:ctrl:result:opt:norm}}
    \vspace{2mm}
    \subfloat[Tracking result of $d$-axis stator current .]{
      \includegraphics[width=\figSize\linewidth]
      {
        src/mearsurement/figures/Fig6.eps
      }%
      \label{fig:ctrl:result:opt:multiplier}}
    \vspace{2mm}
      \subfloat[Control input.]{
        \includegraphics[width=\figSize\linewidth]
        {
          src/mearsurement/figures/Fig8.eps
        }%
        \label{fig:ctrl:result:opt:zeta}}
  \caption{
  Simulation results of the CoNAC (blue) and NAC-AUX (cyan), and reference signal of ${\q}_d$ (red dashed line).
  }
  \label{fig:ctrl:result:opt}
\end{figure}

\begin{figure}[t]
  \centering
      \includegraphics[width=.3\linewidth]
      {
        src/mearsurement/figures/Fig9.eps
      }%
  \caption{
  Simulation results of the CoNAC (blue) and NAC-AUX (cyan), and reference signal of ${\q}_d$ (red dashed line.
  }
  \label{fig:ctrl:result:conrol}
\end{figure}

\subsubsection{System Uncertainty Handling}

The tracking results of the selected controllers are shown in Fig.~\ref{fig: tracking}.
To demonstrate the effectiveness of using DNNs for compensating the lumped system uncertainty function $f$, the gains ${k_q}$ and ${k_z}$ for BSC were intentionally selected as small values, resulting in a weak ability to handle these uncertainties. As a result,
%poor performance and sufficiently large values to satisfy \eqref{eq. ctrl stable condition}.
%the parameters of CM1 are poorly tuned, 
BSC failed to track the reference trajectory, as shown in Fig.~\ref{fig: tracking_CM1}.

@@

\subsection{Input Norm Constraint Handling}\label{sec:sim_cnst}

@@

\subsection{Weight Norm Constraint Handling}

The resulting weight norms of DNN-BSC, DNN-BSC-A, and CoNAC, along with the Lagrange multipliers of CoNAC, are shown in Fig.~\ref{fig: weight and multiplier}. All three controllers—DNN-BSC, DNN-BSC-A, and CoNAC—maintained weight norms within the imposed weight norm constraints.

@@

\section{Constraint Candidates}\label{sec:appen:cstr}

@@

Most physical systems have control input limits due to electrical and mechanical limitations. These are expressed as $\boldsymbol{c}_{\overline \tau}:= [c_{\overline \tau_i}]_{i\in[1,\cdots,n]}$ and $\boldsymbol{c}_{\underline\tau}:= [c_{\underline\tau_i}]_{i\in[1,\cdots,n]}$, where
\begin{equation}
    \begin{aligned}
        c_{\overline \tau_i}=\tau_{(i)} - {\tau_{\overline \tau_i}} \le 0
        \\
        c_{\underline\tau_i}={\tau_{\underline\tau_i}}-\tau_{(i)} \le 0
    \end{aligned}
    \label{eq:cstr:input:bound}
\end{equation}
with $\tau_{\overline \tau_i}$ and $\tau_{\underline\tau_i}$ representing the maximum and minimum control input bounds, respectively.
% The corresponding Lagrange multipliers are $\lambda_{u_j,i},\ \forall j\in[M,m]$. 
The gradients of $\boldsymbol{c}_{\overline \tau}$ and $\boldsymbol{c}_{\underline\tau}$ with respect to $\estwth$ are given by
\begin{equation}
    \begin{aligned}
        \pptfrac{\boldsymbol c_{\overline \tau}}{\estwth}
        =& 
        % \begin{bmatrix}
        %     \pptfrac{c_{\overline \tau_1}}{\estwth}^\top \\
        %     \vdots \\
        %     \pptfrac{c_{\overline \tau_n}}{\estwth}^\top
        % \end{bmatrix}
        = 
            -\pptfrac{\estNN}{\estwth}
        %     \\
        % =&
        =
        -\begin{bmatrix}
            (I_{l_{k+1}}\otimes \estNN_{k}^\top)&
            \!\cdots\! &
            (
                \cdot
            )
        \end{bmatrix} 
        \in
        \mathbb R^{n\times \Xi}
        , 
        \\
        \pptfrac{\boldsymbol c_{\underline\tau}}{\estwth}         
        :=
        & 
        % \begin{bmatrix}
        %     \pptfrac{c_{\underline\tau_1}}{\estwth}^\top \\
        %     \vdots \\
        %     \pptfrac{c_{\underline\tau_n}}{\estwth}^\top
        % \end{bmatrix}
        = 
        +\pptfrac{\estNN}{\estwth}
        % \\
        % =&
        =
        +\begin{bmatrix}
            (I_{l_{k+1}}\otimes \estNN_{k}^\top)&
            % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
            \!\cdots\! &
            (
                \cdot
            )
        \end{bmatrix} 
        \in
        \mathbb R^{n\times \Xi}
        .
    \end{aligned}
    \label{eq:cstr:input:bound:grad}
\end{equation}

@@

Consider the control input $\tau$ as the torque of each actuator corresponding to its generalized coordinate. Since torque is typically linearly proportional to current, actuators that share a common power source are often subject to total current limitations. This can be captured by the following inequality constraint: 
\begin{equation}
    c_{u}=\norm{\mv{\tau}}^2 -\bar\tau^2  \le 0
    \label{eq:cstr:input:norm}
\end{equation}
with $\bar\tau\in\R_{>0}$ denoting the maximum allowable control input magnitude. This input norm constraint is also commonly applied in current and torque control problems for electric motors \cite{Choi:2024aa}.
% The corresponding Lagrangian multipier is $\lambda_{u_b}$. 
The gradients of $c_{u}$ with respect to $\estwth$ are given by
\begin{equation}
    \pptfrac{\boldsymbol c_{u}}{\estwth}
    \!=\! 
    -\textstyle\sum_{i=1}^n 2\tau_{(i)} 
    \left(
        \myrow_i
        (
            -\pptfrac{\estNN}{\estwth}
        )
    \right)^\top  
    \!=\! 
    \tau^\top (I_{l_{k+1}}\otimes \estNN_k^\top)
    \in \mathbb R^{\Xi}.
    \label{eq:cstr:input:norm:grad}
\end{equation}
It should be noted that constraints \eqref{eq. cstr input saturation} and \eqref{eq. cstr input ball} cannot be imposed simultaneously, as their gradients \eqref{eq. nabla input sat} and \eqref{eq. nabla input ball} are linearly dependent, violating the LICQ condition.

>>>>

Consider an uncertain Euler-Lagrange system modeled as
\begin{equation}
    \mm M\ddq + \mm V_m + \mm F + \mm G + \mv\tau_d
    =
    \mysat(\mv\tau)
    \label{eq:sys1}
\end{equation}
where $\q\in \R^n$ denotes the generalized coordinate, $\mv \tau_d$ represents disturbance and $\mv\tau\in\R^n$ denotes the control input. 
The terms $\mm M:=\mm M(\q)\in\R^{n\times n}$, $\mm V_m:=\mm V_m(\q,\dq)\in\R^{n\times n}$, $\mm F:=\mm F(\dq)\in\R^{n}$ and $\mm G:=\mm G(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\mv\tau)}\le \bar\tau$, where $\bar\tau$ denotes the maximum norm of control input.
To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
Appendix \ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.

@@

Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \mm M\fe$. 
Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
\begin{equation}
    \begin{aligned}
        \ddtt{V}_1
        =&
        \fe^\top \mm M (
            -\mm V_m \fe -\mm K \fe + \mv f
            -\mv \tau_d + \mysat(\mv\tau)
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top \dot{\mm M}\fe
        \\
        =&
        -
        \fe^\top \mm K \fe 
        +
        \fe^\top (
            \mv f+\mysat(\mv\tau)
            -\mv \tau_d
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top(\dot{\mm M}- 2\mm V_m)\fe
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \bar\tau_d\norm{\fe}
        +
        \fe^\top (\mv f+\mysat(\mv \tau))
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \bar\tau_d\norm{\fe}
        +
        \fe^\top (\mysat(\mv\tau)-\mv\tau^*)
        ,
    \end{aligned}
    \label{eq:lya1:dot1}
\end{equation}
where $\mv\tau^*:= -\mv f$ is the ideal control input whose maximum norm is $\bar\tau$ according to Assumption \ref{assum:feasible} and $\mysat(\cdot)$. 
Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_{\min}(\mm K)}$, if $\mv \tau=-\mv\tau^*$ can be realized.
However, $\mv \tau^*$ is not available in practice, since $\mv f$ is unknown.

@@

% ------------------------------------
% Robot Model and Reference Trajectory
% ------------------------------------
The proposed CoNAC was validated using a two-link manipulator model, as depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{Markus:2013aa}. 
The system dynamics of the two-link manipulator is described by the following equations:
\MSRY{ADD MORE DETAIL; Following Eqn is just example}
\begin{equation}
    \begin{aligned}
        \mm M(\q) \ddtt{\q} + \mm V_m(\q,\dot\q) + \mm F(\q,\dot\q) + \mm G(\q) = \mv\tau,
        \\
        \mv\tau = \estNN(\q,\dot\q),
    \end{aligned}
    \label{eq:robot_dynamics}
\end{equation}
The parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ \MSRY{more parameters} denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
The values of the system model parameters are provided in Table~\ref{table:system:params}. 
The desired trajectory for $\q=[q_1,q_2]^\top $ was defined with \MSRY{5th Poly functions} as
\begin{equation}
    \qd(t) = 
    \begin{bmatrix}
        {q_d}_1\\{q_d}_2
    \end{bmatrix}
    =
    \begin{cases}
    \mypoly({\qd}_0,{\qd}_1,t_f,t)
        & \text{if } 0\le t < t_f \\
    \mypoly({\qd}_1,{\qd}_2,t_f,t-t_f)
        & \text{if } t_f\le t < 2t_f \\
    \mypoly({\qd}_2,{\qd}_1,t_f,t-2t_f)
        & \text{if } 2t_f\le t < 3t_f \\
    \mypoly({\qd}_1,{\qd}_0,t_f,t-3t_f)
        & \text{if } 3t_f\le t < 4t_f \\
    \end{cases}
    ,
    \label{eq:desired trajectory}
\end{equation}
where \MSRY{CAN BE CHANGED}$\q_0=[0,0]^\top$, $\q_1=[\pi/2,\pi/2]^\top$, $\q_2=[\pi/2,0]^\top$, and $t_f=5$ s.
\MSRY{VIDEO IS PROVIDED; IF WE CAN PROVIDE}

% ------------------------------------
% Control Input Saturation
% ------------------------------------
To demonstrate the effectiveness of the proposed CoNAC to handle the combination of the nonlinear input constraints, the following control input saturations were imposed:
\begin{equation}
    \mysat(\mv\tau)
    :=
    \begin{cases}
        \mv\tau, 
        & 
        \text{if } \Vert\mv\tau\Vert\le \bar\tau,
        \\
        \bar\tau
        \cdot
        \tfrac{\mv\tau}{\Vert\mv\tau\Vert}, 
        & 
        \text{otherwise},
    \end{cases}
    \label{eq:sat}
\end{equation}
where $\bar\tau=50, \bar\tau_1$ and $\bar\tau_2$ are the saturation limit values for the norm of the control input and the first and second links, respectively.

@@

% ------------------------------------
% Controller Table
% ------------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Properties of the controllers used in simulation}
    \label{table:controller}
    \centering
    \begin{tabular}{c c c}
    \hline
        & \multicolumn{2}{c}{\bf{Handling Capability}}\\
        & Weight Norm Constraint & Input Norm Constraint\\
    \hline
    \hline
    \multirow{2}{*}{\bf{CoNAC}} & O & O \\
        & (by optimization) &  (by optimization)\\
    \hline
    \multirow{2}{*}{\bf{NAC-AUX}} & O & $\triangle$ \\
        & (by optimization) & (by aux. system)\\
    \hline
    \end{tabular}
\end{table}

@@

\begin{figure}[t]
  \centering
    \subfloat[Tracking result of $q_1$.]{
      \includegraphics[width=\figSize\linewidth]
      {
        src/measurement/figures/Fig1.eps
      }%
      \label{fig:ctrl:result:q1}}
    \vspace{2mm}
    \subfloat[Tracking result of $q_2$.]{
      \includegraphics[width=\figSize\linewidth]
      {
        src/measurement/figures/Fig2.eps
      }%
      \label{fig:ctrl:result:q2}}
    \vspace{2mm}
      \subfloat[Control input $\tau_1$.]{
        \includegraphics[width=\figSize\linewidth]
        {
          src/measurement/figures/Fig3.eps
        }%
        \label{fig:ctrl:result:tau:1}}
    \vspace{2mm}
      \subfloat[Control input $\tau_2$.]{
        \includegraphics[width=\figSize\linewidth]
        {
          src/measurement/figures/Fig4.eps
        }%
        \label{fig:ctrl:result:tau:2}}
  \caption{
  Simulation results of the CoNAC (blue) and NAC-AUX (cyan), and reference signal of $\qd$ (red dashed line).
  }
\label{fig:ctrl:result}
\end{figure}

\begin{figure}[t]
  \centering
    \subfloat[Norm of weights $\hat\theta_i$.]{
      \includegraphics[width=\figSize\linewidth]
      {
        src/measurement/figures/Fig5.eps
      }%
      \label{fig:ctrl:result:opt:norm}}
    \vspace{2mm}
    \subfloat[Lagrange multipliers $\lambda_j$ in logarithmic scale.]{
      \includegraphics[width=\figSize\linewidth]
      {
        src/measurement/figures/Fig6.eps
      }%
      \label{fig:ctrl:result:opt:multiplier}}
    \vspace{2mm}
      \subfloat[Auxiliary states $\mv{\zeta}$ of NAC-AUX.]{
        \includegraphics[width=\figSize\linewidth]
        {
          src/measurement/figures/Fig8.eps
        }%
        \label{fig:ctrl:result:opt:zeta}}
  \caption{
  ...
  }
  \label{fig:ctrl:result:opt}
\end{figure}

\begin{figure}[t]
  \centering
      \includegraphics[width=\figSize\linewidth]
      {
        src/measurement/figures/Fig9.eps
      }%
  \caption{
Control input $\tau$ in time interval $[??, ??]$ s (bird's eye view).
  }
  \label{fig:ctrl:result:conrol}
\end{figure}

% ------------------------------------
% Tracking Performance
% ------------------------------------
\subsubsection{Learning Capability of Neural Network}

The tracking results of CoNAC and NAC-AUX are shown in Fig.~\ref{fig:ctrl:result}.
To demonstrate the effectiveness of using DNNs for compensating the lumped system uncertainty function $f$, the gains ${k_q}$ and ${k_z}$ for BSC were intentionally selected as small values, resulting in a weak ability to handle these uncertainties. As a result,
BSC failed to track the reference trajectory, as shown in Fig.~\ref{fig: tracking_CM1}.

@@

% ------------------------------------
% Control Input Saturation
% ------------------------------------
\subsubsection{Input Constraint Handling}

@@

% ------------------------------------
% Weight Norm Constraint Handling
% ------------------------------------
The resulting weight norms of DNN-BSC, DNN-BSC-A, and CoNAC, along with the Lagrange multipliers of CoNAC, are shown in Fig.~\ref{fig: weight and multiplier}. All three controllers—DNN-BSC, DNN-BSC-A, and CoNAC—maintained weight norms within the imposed weight norm constraints.

@@

\section{Input Constraint Candidates}\label{sec:appen:cstr}

@@

Most physical systems have control input limits due to electrical and mechanical limitations. These are expressed as $\boldsymbol{c}_{\overline \tau}:= [c_{\overline \tau_i}]_{i\in[1,\cdots,n]}$ and $\boldsymbol{c}_{\underline\tau}:= [c_{\underline\tau_i}]_{i\in[1,\cdots,n]}$, where
\begin{equation}
    \begin{aligned}
        c_{\overline \tau_i}=\tau_{(i)} - {\tau_{\overline \tau_i}} \le 0
        \\
        c_{\underline\tau_i}={\tau_{\underline\tau_i}}-\tau_{(i)} \le 0
    \end{aligned}
    \label{eq:cstr:input:bound}
\end{equation}
with $\tau_{\overline \tau_i}$ and $\tau_{\underline\tau_i}$ representing the maximum and minimum control input bounds, respectively.
% The corresponding Lagrange multipliers are $\lambda_{u_j,i},\ \forall j\in[M,m]$. 
The gradients of $\boldsymbol{c}_{\overline \tau}$ and $\boldsymbol{c}_{\underline\tau}$ with respect to $\estwth$ are given by
\begin{equation}
    \begin{aligned}
        \pptfrac{\boldsymbol c_{\overline \tau}}{\estwth}
        =& 
        \begin{bmatrix}
            \pptfrac{c_{\overline \tau_1}}{\estwth}^\top \\
            \vdots \\
            \pptfrac{c_{\overline \tau_n}}{\estwth}^\top
        \end{bmatrix}
        = 
            +\pptfrac{\estNN}{\estwth}
        %     \\
        % =&
        =
        +
        \begin{bmatrix}
            (I_{l_{k+1}}\otimes \estact_{k}^\top)&
            \!\cdots\! &
            (
                \cdot
            )
        \end{bmatrix} 
        \in
        \mathbb R^{n\times \Xi}
        , 
        \\
        \pptfrac{\boldsymbol c_{\underline\tau}}{\estwth}         
        =
        & 
        \begin{bmatrix}
            \pptfrac{c_{\underline\tau_1}}{\estwth}^\top \\
            \vdots \\
            \pptfrac{c_{\underline\tau_n}}{\estwth}^\top
        \end{bmatrix}
        = 
        -\pptfrac{\estNN}{\estwth}
        % \\
        % =&
        =
        -\begin{bmatrix}
            (I_{l_{k+1}}\otimes \estact_{k}^\top)&
            % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
            \!\cdots\! &
            (
                \cdot
            )
        \end{bmatrix} 
        \in
        \mathbb R^{n\times \Xi}
        .
    \end{aligned}
    \label{eq:cstr:input:bound:grad}
\end{equation}

@@

Consider the control input $\tau$ as the torque of each actuator corresponding to its generalized coordinate. Since torque is typically linearly proportional to current, actuators that share a common power source are often subject to total current limitations. This can be captured by the following inequality constraint: 
\begin{equation}
    c_{u}=\norm{\mv{\tau}}^2 -\bar\tau^2  \le 0
    \label{eq:cstr:input:norm}
\end{equation}
with $\bar\tau\in\R_{>0}$ denoting the maximum allowable control input magnitude. This input norm constraint is also commonly applied in current and torque control problems for electric motors \cite{Choi:2024aa}.
% The corresponding Lagrangian multiplier is $\lambda_{u_b}$. 
The gradients of $c_{u}$ with respect to $\estwth$ are given by
\begin{equation}
    \pptfrac{\boldsymbol c_{u}}{\estwth}
    \!=\! 
    \textstyle\sum_{i=1}^n 2\tau_{(i)} 
    \left(
        \myrow_i
        (
            \pptfrac{\estNN}{\estwth}
        )
    \right)^\top  
    \!=\! 
    {\pptfrac{\estNN}{\estwth}}^\top
    \mv{\tau}
    % \tau^\top (I_{l_{k+1}}\otimes \estNN_k^\top)
    \in \mathbb R^{\Xi}.
    \label{eq:cstr:input:norm:grad}
\end{equation}
It should be noted that constraints \eqref{eq:cstr:input:bound} and \eqref{eq:cstr:input:norm} can be imposed simultaneously, as their gradients \eqref{eq:cstr:input:bound:grad} and \eqref{eq:cstr:input:norm:grad} are linearly independent, satisfying the LICQ condition.
